TODO: title

### 2014-04-21 paper/main.tex
set up to start writing

OUTLINE

1. Introduction
  [story]
    New user experiance is important
      new users are needed to maintine usage of a site as older users leave the system
      all users are new users at some time
      new user experiance may set the expectation for how the system behaves in the future. (Citation of this may be important)

2. Background
3. Methodology
4. Experiments %Not a fan of this title.
  4.1 RMSE by profile size
  4.2 Soft metrics
  4.3 Value of implicit information
5. conclusions

>>>>

\documentclass[letterpaper]{sig-alternate}

\pdfpagewidth=8.5in
\pdfpageheight=11in

%\usepackage[factor=250,spacing=true]{microtype}

\begin{document}
\conferenceinfo{RecSys '14}{October 6--10, 2014, Foster City, Silicon Valley, USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.

\title{TODO: title}

\numberofauthors{2}

\author {
\alignauthor
Daniel Kluver\\
\affaddr{GroupLens Research}\\
\affaddr{Department of Computer Science and Engineering}\\
\affaddr{University of Minnesota}\\
\affaddr{Minneapolis, MN 55455 USA}\\
\email{kluver@cs.umn.edu}
\alignauthor
Joseph A. Konstan\\
\affaddr{GroupLens Research}\\
\affaddr{Department of Computer Science and Engineering}\\
\affaddr{University of Minnesota}\\
\affaddr{Minneapolis, MN 55455 USA}\\
\email{konstan@cs.umn.edu}
}

\maketitle
\begin{abstract}

TODO: abstract

\end{abstract}

%TODO: update these things.
% A category with the (minimum) three required fields
\category{H.4}{Information Systems Applications}{Miscellaneous}
%A category including the fourth, optional field follows...
\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

%TODO: update these things.
\terms{Theory}

%TODO: update these things.
\keywords{ACM proceedings, \LaTeX, text tagging}

\section{Introduction}
\section{Methodology}
\section{Results}
\section{Conclusions}

\section{Acknowledgements}
 \cite{harper2005economic}
 TODO:

\bibliographystyle{abbrv}
\bibliography{resources}  % sigproc.bib is the name of the Bibliography in this case

\end{document}
